Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-01-21 writeup/gz_hubble_data.tex
Small additions to write up; adding sections

\newcommand{\ferengi}{\textsc{ferengi}}

@@

This will be the data release paper for GZ Hubble. We present the classifications, the methodology for data reduction and corrections for redshift dependent biases in the observed morphologies.

@@

@@

The votes of individual users who classified galaxies in Galaxy Zoo Hubble are combined to make a vote fraction for each question on the classification tree. Users votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights. The majority of users have weights very close to 1.0 ({\bf STEVEN: Is this true for GZH - do you have a plot of the distribution of user weights or consistencies we can include here?}.

@@

Previous version of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which are typically at $z<0.1$. In these cases it could be assumed that there was no real evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was assumed to be due to the effects of redshift on the image quality (\ie. the reduction in physical resolution, surface brightness dimming etc). So for both previous releases of GZ morphogloies, a correction was provided for redshift dependent bias based on matching the classification fractions at the highest redshfts with those at the lowest redshift. See \citet{bam09} and \citet{wil13} for the details.

In the GZH samples the redshift range is so large that we expect to find redshift evolution of the types and morphologies of galaxies which are seen. So the previous methods of correcting for redshift dependent bias will not work. In addition the effects of band shifting will change the images even more across these redshift ranges. %Figure~\ref{exampleFERENGI} illustrates some of the possible effects of losing features in spiral galaxies at high redshift.

%-----------------------------------------------------------------------------------------------------------------------------------
%\begin{figure}
%\begin{center}
%\includegraphics[width=60mm]{figures/example_ferengi2.pdf}
%\caption{Examples of an obvious spiral and obvious elliptical at $z=0$ which both look similar when redshifted to $z=0.8$. See below for the description of the method for redshifting.\label{exampleFERENGI}}
%\end{center}
%\end{figure}
 %-----------------------------------------------------------------------------------------------------------------------------------

In order to test the effects of redshift we made images of the same galaxy at a variety of redshifts using input images from the SDSS \citep{yor00,str02} and the \ferengi{} code \citep{bar08a} to produce images that match the observational properties of those observed in the HST surveys. These images were classified in the Galaxy Zoo interface using the same classification scheme as the original HST images.

@@

\begin{table*}
\caption{Summary of morphological categories selected for FERENGI sample. \hl{For Edmond: does $p_{\rm obvious/dominant}>0.5$ mean ($p_{\rm obv}+p_{\rm dom}>0.5$) or ($p_{\rm ob}$ OR $p_{\rm dom} >0.5$)?}\label{morphologies}}
\begin{tabular}{lllc}
\hline\hline
Morphology          & Label &  Selection                                                                                            & $N_{\rm objects}$ \\
                    &       &                                                                                                       & [$N_z \times N_\mu$] \\
\hline
Features            & Yes   & $p_{\rm features} > 0.8$, $p_{\rm odd} < 0.1$                                                         & 12 \\ 
                    & Int   & $0.3 < p_{\rm smooth} < 0.6$, $p_{\rm odd} < 0.1$                                                     & 12 \\ 
                    & No    & $p_{\rm smooth} > 0.8$, $p_{\rm odd} < 0.1$                                                           & 12 \\ 
Merger              & No    & $p_{\rm features} > 0.8$, $p_{\rm odd < 0.1}$, $p_{\rm merger} < 0.1$                                 & 12 \\
                    & Int   & $p_{\rm odd} > 0.5$, $0.1< p_{\rm merger} < 0.4$                                                      & 12 \\ 
                    & Yes   & $p_{\rm odd} > 0.5$, $p_{\rm merger} > 0.4$                                                           & 12 \\
Edge-on             & Yes   & $p_{\rm edgeon} > 0.8$, $p_{\rm features} > 0.5$                                                      & 12 \\
                    & Int   & $0.4 < p_{\rm edgeon} < 0.8$ , $p_{\rm features} > 0.5$                                               & 12 \\
                    & No    & $p_{\rm edgeon} < 0.2$, $p_{\rm features} > 0.5$                                                      & 12 \\
Bar                 & No    & $p_{\rm bar} < 0.1$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
                    & Int   & $0.2 < p_{\rm bar} < 0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                           & 24 \\
                    & Yes   & $p_{\rm bar} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
Visible spiral      & No    & $p_{\rm spiral} < 0.2$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
                    & Int   & $0.2 < p_{\rm spiral} < 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$   & 12 \\
                    & Yes   & $p_{\rm spiral} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
Oblique bulge size  & No    & $p_{\rm nobulge>0.6}$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$          & 12 \\
                    & Int   & $p_{\rm justnoticeable}>0.6$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$   & 12 \\
                    & Yes   & $p_{\rm obvious/dominant}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$ & 12 \\
Edge-on bulge shape & Round & $p_{\rm rounded}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
                    & Boxy  & $p_{\rm boxy}>0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.2$                                  & 12 \\
                    & Non   & $p_{\rm nobulge}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
\hline\hline
\end{tabular}
\end{table*}

In addition to the physical parameters of the input images, the \ferengi{} output depends on assumptions of the global galaxy evolution model. This evolution is a crude mechanism that mimics the brightness increase of galaxies with increasing redshift (out to at least $z\sim1-2$). The effect on the redshifted images is simply an empirical addition to the magnitude of a galaxy of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and $e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially brightens the galaxy by 1~magnitude by $z=1$). We ran \ferengi{} for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments of $\Delta e = 0.5$. Figure~\ref{exampleFERENGI} shows several examples of the effects of ``losing`` spiral/disc features with increasing redshift for two galaxies with $e=0$.

The final number of \ferengi{} images produced for each galaxy is a ultimately a function of galaxy's redshift, since the code cannot resample the images at better angular resolution than the original SDSS data, and the number of $e$ values selected. Table~\ref{ferengivalues} summarizes the total sample of redshifted images produced for GZ: Hubble.

@@

\begin{figure*}
\includegraphics[width=160mm]{figures/example_ferengi.pdf}
\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images. The value of $p_{\rm features}$ for each panel is (1) Top row: $p_{\rm features}=$ 0.9, 0.625, 0.35, 0.35, 0.225 and (2) Bottom row: $p_{\rm features}=$ 1.00, 0.875, 0.875, 0.625, 0.375. \label{exampleFERENGI}}
\end{figure*}

@@

The approach used in GZH for correcting the weighted classifications for user bias rests on the assumption that the \emph{amount} of bias is a function of the apparent size and brightness of the image as seen on screen. This is controlled by two types of parameters: \textbf{intrinsic} properties of the galaxy itself, such as its physical diameter and luminosity, and \textbf{extrinsic} properties, such as the distance (redshift) of the galaxy and its relative orientation. There are likely other parameters that affect user accuracy, such as the proximity of close companions \citep[``distraction bias''; see][]{joh15} or those that vary by individual user. The combination of all such parameters forms a high-dimensional space, and we have insufficient test galaxies to measure the individual effects of each. Instead, we use just two parameters that are intended to capture the bulk of the change in bias (based on GZ1/GZ2): a galaxy's $r^\prime$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$; extrinsic).

The change in bias as a function of $\mu_r$ and $z$ is measured using the \ferengi{} images over all the evolutionary corrected factors. We assume that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for a galaxy can be expressed as:

@@

\noindent where $f_{\mu,z=0.3}$ is the ``calibrated'' vote fraction at the lowest redshift in the \ferengi{} bins, which is at redshift $z=0.3$ and $\zeta$ is a positive parameter that controls the rate at which $f$ drops off with increasing redshift. This formula fits the data relatively well (with almost no exceptions, the vote fractions for featured galaxies decrease monotonically with increasing redshift), and the exponential function bounds the observed vote fractions between $f_{\mu,z=0.3}$ and zero. Figure~\ref{fig:zeta_examples} show examples of the change in vote fraction and their fits to Equation~\ref{eqn:fzeta} for a random selection of galaxies in the \ferengi{} images.

@@

We then take the values of $\zeta$ for \emph{all} sets of artifically redshifted galaxies and use them to fit the overall distribution of $\zeta$ as a function of surface brightness (since we expect the correction being applied to vary as a function of the intrinsic galaxy properties). We restrict the galaxies that can be used to measure the calibration to those with data at the pivot redshift of $z=0.3$, those with non-zero $f_\textrm{features}$ at $z=0.3$, and with a reasonable fit to the exponential model ($\Delta \chi^2 > 3.0$).

Figure~\ref{fig:zeta_mu} shows the results of the sample; the correction is a weak function of surface brightness overall. Higher-surface brightness galaxies have stronger average corrections, likely because these galaxies are more likely to have larger $f_\textrm{features}$ values at high redshifts. Low surface brightness galaxies are more likely to begin low and remain low; the bounded nature of the dropoff (and Poissonian-like variance among the individual voters) means that the average magnitude of $\zeta$ will be less.

@@

\noindent where $\hat\zeta$ is the correction factor that will be applied to each galaxy as a function of surface brightness. The best-fit parameters to the linear fit (from least-squares optimization) are $\zeta_0 = 0.1, \zeta_1=1.4$. To make the final debiased correction, we modify the simple exponential form of Equation~\ref{eqn:fzeta} to bound the debiased vote fractions between $f$ and 1:

\begin{equation}
f_\textrm{debiased} = 1 - (1 - f)e^{\frac{z-z_0}{\hat\zeta}}.
\label{eqn:fzeta_mod}
\end{equation}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/eye_of_sauron.pdf}
\caption{Surface brightness vs. redshift of 118,083 galaxies in the ACS Hubble sample. The white grid denotes the surface brightness and redshift range of the \ferengi{} images, subdivided in bins corresponding to fixed ranges used for analysis in Figure~\ref{fig:p_vs_p}.}

@@

In Figure~\ref{fig:p_vs_p} we examine the change in $p_{\rm features}$ for the \ferengi{} galaxies relative to their lowest simulated redshift. In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{ferengivalues}), and only those which had detectable surface brightness measurements in Sextractor; this includes 3,959 of the total 6,466 images. For each simulated redshift value $z$, and at fixed surface brightness $\mu$, we plot $p_{\rm features,z}$, the value measured at that simulated redshift, vs $p_{\rm features,z=0.3}$, the value measured for the same galaxy imaged at $z=0.3$.

Our objective is to use these data to predict, for a galaxy with a measured $p_{\rm features,z}$ value, what its $p_{\rm features}$ value would have been if it had been viewed at $z=0.3$. This predicted value is defined as the debiased vote fraction $p_{\rm features,debiased}$, and is calculated by applying a correction to the measured value of $p_{\rm features}$, determined by the $\zeta$ function described in the previous section. We determine that a predicted value can be obtained so long as the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ is single-valued; that is, for a given $p_{\rm features,z}$, there is one corresponding value of $p_{\rm features}$ at $z=0.3$.

In Figure~\ref{fig:p_vs_p} we see that the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ is \emph{not} always single valued; hence we do not find it appropriate to correct galaxies that lie in these regions of surface brightness/redshift/$p_{\rm features}$ space. These regions tend to have low $p_{\rm features}$ values at high redshift, but a wide range of values at $z=0.3$. These regions contain two morphological types of galaxies: First are genuine ellipticals, which have low values of $p_{\rm features}$ at both high and low redshift. Second are disks whose features become washed out at high redshift; hence their $p_{\rm freatures}$ value at $z=0.3$ may be quite high, while the value observed at high redshift is very low. This effect is strongest at the highest redshift and the lowest surface brightnesses, where features become near impossible to discern from the images. From this information we conclude that, for the Hubble galaxies, we cannot distinguish between genuine ellipticals and disks if the measured value of $p_{\rm features}$ is too low for a given surface brightness and redshift, because the relationship between the measured value and the ``original'' ($z=0.3$) value is not single-valued.

@@

\begin{table*}
\caption{Breakdown of what we can correct out of the Hubble data, by sample. \label{hubble_debiasable}}
\begin{tabular}{lrrrrrrr}
\hline\hline
                                   & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & SDSS    & Total \\
\hline
Correctable                        & 2,325   & 20,669 & 2,748 & 1,074  & 1,022   & 0       & 27,838\\
Uncorrectable                      & 1,403   & 19,626 & 1,832 & 271    & 980     & 0       & 24,112\\
No Correction Needed ($z \le 0.3$) & 967     & 11,693 & 1,190 & 280    & 247     & 37,545  & 51,922\\ 
NEI                                & 2,465   & 33,727 & 1,886 & 691    & 2,023   & 0       & 40,792\\
No Redshift Information            & 1,347   & 7,093  & 1,648 & 235    & 641     & 14,316  & 25,280\\
Total                              & 8,507   & 92,808 & 9,304 & 2,551  & 4,913   & 51,861  & 169,944\\
\hline\hline
\end{tabular}
\end{table*}

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
\caption{Distributions of redshift, surface brightness, and $p_{features}$ for correctable (purple), uncorrectable (green), and NEI (pink) galaxies in the full Hubble sample. The uncorrectable galaxies tend towards higher redshift, slightly lower in surface brightness, and lower values of $p_{features}$ than the correctable galaxies. The long tail of NEI galaxies in redshift and surface brightness demonstrates the limits of the \ferengi{} sample, for which there is no data at $z>1$ or $\mu>24$.}
\label{fig:z_mu_p}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
\caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), uncorrectable (middle), and NEI (right) galaxies in the Hubble sample.}

@@

\subsection{Results of FERENGI Analysis}

We show here the {\bf preliminary} results of citizen scientist classifications of images of galaxies placed at artificial redshifts. Figure~\ref{fig:ferengi_results_fake} shows the {\bf preliminary} range of change of vote fractions for the change of $p_{\rm features}$ with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the colour).

%-----------------------------------------------------------------------------------------------------------------------------------
\begin{figure}
\begin{center}

\includegraphics[width=0.45\textwidth]{figures/somewhat_fake_results.pdf}

\caption{Preliminary results of the \ferengi{} redshifting exercise. WARNING NO USER WEIGHTING.... For a range of vote fraction levels with three surface-brightness levels and 7 evolutionary corrections each (the colours indicate evolutionary correction value with green being $e=0$, we show the range of evolution of the vote fractions for featured vs. smooth with redshift.}

\label{fig:ferengi_results_fake}

\end{center}
\end{figure}
%-----------------------------------------------------------------------------------------------------------------------------------

@@

@@

\subsection{SDSS images}

@@

Now people go and do science with these awesome Galaxy Zoo Hubble classifications.

@@

@@

Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S. Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England. The SDSS Web Site is http://www.sdss.org/.

>>>>

\newcommand{\ferengi}{\textsc{ferengi}}
\newcommand{\sextractor}{\textsc{sextractor}}

@@

This will be the data release paper for GZ:Hubble. We present the classifications, the methodology for data reduction and corrections for redshift dependent biases in the observed morphologies.

@@

Needs: coordinate/location description.

So GZ:CANDELS overlaps with GZ:Hubble in GOODS-S and COSMOS. GZH doesn't

@@

The votes of individual users who classified galaxies in GZH are combined to make a vote fraction for each question on the classification tree. Users' votes are weighted slightly \citep[in a method identical to that described in][]{wil13} such that users who frequently disagree with all other users end up having very low weights. The majority of users have weights very close to $w=1.0$ ({\bf STEVEN: Is this true for GZH - do you have a plot of the distribution of user weights or consistencies we can include here?}.

@@

The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which are typically at $z<0.1$. In these cases it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie. the reduction in physical resolution, surface brightness dimming, etc). For both previous releases of GZ morphologies, we provided a correction for redshift-dependent bias based on matching the classification fractions at the highest redshfts with those at the lowest redshift. See \citet{bam09} and \citet{wil13} for the details.

In the GZH samples, the redshift range is large enough that we expect to measure cosmological evolution of the types and morphologies of galaxies in the sample. As a result, the previous methods of correcting for redshift dependent bias will not work. In addition, the effects of band shifting will change the images even more across these redshift ranges. %Figure~\ref{fig:exampleFERENGI} illustrates some of the possible effects of losing features in spiral galaxies at high redshift.

%-----------------------------------------------------------------------------------------------------------------------------------
%\begin{figure}
%\begin{center}
%\includegraphics[width=60mm]{figures/example_ferengi2.pdf}
%\caption{Examples of an obvious spiral and obvious elliptical at $z=0$ which both look similar when redshifted to $z=0.8$. See below for the description of the method for redshifting.\label{fig:exampleFERENGI}}
%\end{center}
%\end{figure}
 %-----------------------------------------------------------------------------------------------------------------------------------

In order to test and correct for the effects of redshift, we generated a set of calibration images. These images consist of the same galaxy as it would appear over a variety of redshifts. The input images are from the SDSS \citep{yor00,str02} and are processed using the \ferengi{} code \citep{bar08a} to match the observational properties of the HST surveys out to $z=1$. These images were classified in the Galaxy Zoo interface using the same classification scheme as the original HST images.

@@

\begin{table*}
\caption{Summary of morphological categories selected for FERENGI sample.\label{morphologies}}
\begin{tabular}{lllc}
\hline\hline
Morphology          & Label &  Selection                                                                                            & $N_{\rm objects}$ \\
                    &       &                                                                                                       & [$N_z \times N_\mu$] \\
\hline
Features            & Yes       & $p_{\rm features} > 0.8$, $p_{\rm odd} < 0.1$                                                         & 12 \\ 
                    & Int.      & $0.3 < p_{\rm smooth} < 0.6$, $p_{\rm odd} < 0.1$                                                     & 12 \\ 
                    & No        & $p_{\rm smooth} > 0.8$, $p_{\rm odd} < 0.1$                                                           & 12 \\ 
Merger              & No        & $p_{\rm features} > 0.8$, $p_{\rm odd < 0.1}$, $p_{\rm merger} < 0.1$                                 & 12 \\
                    & Int.      & $p_{\rm odd} > 0.5$, $0.1< p_{\rm merger} < 0.4$                                                      & 12 \\ 
                    & Yes       & $p_{\rm odd} > 0.5$, $p_{\rm merger} > 0.4$                                                           & 12 \\
Edge-on             & Yes       & $p_{\rm edgeon} > 0.8$, $p_{\rm features} > 0.5$                                                      & 12 \\
                    & Int.      & $0.4 < p_{\rm edgeon} < 0.8$ , $p_{\rm features} > 0.5$                                               & 12 \\
                    & No        & $p_{\rm edgeon} < 0.2$, $p_{\rm features} > 0.5$                                                      & 12 \\
Bar                 & No        & $p_{\rm bar} < 0.1$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
                    & Int.      & $0.2 < p_{\rm bar} < 0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                           & 24 \\
                    & Yes       & $p_{\rm bar} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$                                 & 24 \\
Visible spiral      & No        & $p_{\rm spiral} < 0.2$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
                    & Int.      & $0.2 < p_{\rm spiral} < 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$   & 12 \\
                    & Yes       & $p_{\rm spiral} > 0.8$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.2$, $p_{\rm bar} < 0.1$         & 12 \\
Oblique bulge size  & No        & $p_{\rm nobulge>0.6}$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$          & 12 \\
                    & Int.      & $p_{\rm justnoticeable}>0.6$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$   & 12 \\
                    & Yes       & $p_{\rm obvious|dominant}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} < 0.5$, $p_{\rm bar} < 0.2$ & 12 \\
Edge-on bulge shape & Round     & $p_{\rm rounded}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
                    & Boxy      & $p_{\rm boxy}>0.4$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.2$                                  & 12 \\
                    & No bulge  & $p_{\rm nobulge}>0.5$, $p_{\rm features} > 0.5$, $p_{\rm edgeon} > 0.5$                               & 12 \\
\hline\hline
\end{tabular}
\end{table*}

In addition to the physical parameters of the input images, the \ferengi{} output depends on assumptions of the global galaxy evolution model. This evolution is a crude mechanism that mimics the brightness increase of galaxies with increasing redshift (out to at least $z\sim1-2$). The effect on the redshifted images is simply an empirical addition to the magnitude of a galaxy of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and $e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially brightens the galaxy by 1~magnitude by $z=1$). We ran \ferengi{} for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows several examples of the effects of ``losing`` spiral/disc features with increasing redshift for two galaxies with $e=0$.

The final number of \ferengi{} images produced for each galaxy is ultimately a function of galaxy's redshift, since the new images cannot be resampled at better angular resolution than the original SDSS data, as well as the number of $e$ values selected. Table~\ref{ferengivalues} summarizes the total sample of redshifted images produced for GZH.

@@

\begin{figure*}
\includegraphics[width=160mm]{figures/example_ferengi.pdf}
\caption{Examples of two galaxies which have been run through the FERENGI code to produce simulated HST images. The value of $p_{\rm features}$ for each panel is (1) Top row: $p_{\rm features}=$ 0.9, 0.625, 0.35, 0.35, 0.225 and (2) Bottom row: $p_{\rm features}=$ 1.00, 0.875, 0.875, 0.625, 0.375. \label{fig:exampleFERENGI}}
\end{figure*}

@@

The approach used in GZH for correcting the weighted classifications for user bias rests on the assumption that the \emph{amount} of bias is a function of the apparent size and brightness of the image as seen on screen. This is controlled by two types of parameters: \textbf{intrinsic} properties of the galaxy itself, such as its physical diameter and luminosity, and \textbf{extrinsic} properties, such as the distance (redshift) of the galaxy and its relative orientation. There are likely other parameters that affect user accuracy, such as the proximity of close companions \citep[``distraction bias''; see][]{joh15} or bias as a function of the individual user. The combination of all such parameters forms a high-dimensional space, and we have insufficient data to measure their individual effects. Instead, we use just two parameters that are intended to capture the bulk of the change in bias (based on GZ1/GZ2): a galaxy's $r^\prime$-band surface brightness ($\mu_r$; intrinsic) and redshift ($z$; extrinsic).

The change in bias as a function of $\mu_r$ and $z$ is measured using the \ferengi{} images over all the evolutionary correction factors. We assume that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for a galaxy can be expressed as:

@@

\noindent where $f_{\mu,z=0.3}$ is the ``calibrated'' vote fraction at the lowest redshift in the \ferengi{} bins ($z=0.3$) and $\zeta$ is a positive parameter that controls the rate at which $f$ decreases with increasing redshift. This formula fits the data relatively well (with almost no exceptions, the vote fractions for featured galaxies decrease monotonically with increasing redshift), and the exponential function bounds the observed vote fractions between $f_{\mu,z=0.3}$ and zero. Figure~\ref{fig:zeta_examples} show examples of the change in vote fraction and their fits to Equation~\ref{eqn:fzeta} for a random selection of galaxies in the \ferengi{} images.

@@

We use the values of $\zeta$ for \emph{all} sets of artifically redshifted galaxies to fit the overall distribution as a function of surface brightness, since we expect the correction being applied to vary as a function of the intrinsic galaxy properties. We restrict the galaxies that can be used to measure the calibration to those with data at the pivot redshift of $z=0.3$, non-zero $f_\textrm{features}$ at $z=0.3$, and with a reasonable fit to the exponential model ($\Delta \chi^2 > 3.0$).

Figure~\ref{fig:zeta_mu} shows the results of fitting the \ferengi{} images with Equation~\ref{eqn:fzeta}; the correction is a weak function of galaxy surface brightness. Higher-surface brightness galaxies have stronger average corrections, likely because these galaxies are more likely to have larger $f_\textrm{features}$ values at high redshifts. Low surface brightness galaxies are more likely to begin low and remain low; the bounded nature of the dropoff (and Poissonian-like variance among the individual voters) means that the average magnitude of $\zeta$ will be less.

@@

\noindent where $\hat\zeta$ is the correction factor applied to each galaxy as a function of surface brightness. The best-fit parameters to the linear fit (from least-squares optimization) are $\zeta_0=0.1$, $\zeta_1=1.4$. To make the final debiased correction, we modify the simple exponential form of Equation~\ref{eqn:fzeta} to bound the debiased vote fractions between $f$ and 1:

\begin{equation}
f_\textrm{features,debiased} = 1 - (1 - f)e^{\frac{z-z_0}{\hat\zeta}}.
\label{eqn:fzeta_mod}
\end{equation}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/eye_of_sauron.pdf}
\caption{Surface brightness vs. redshift of 118,083 galaxies in the ACS sample. The white grid denotes the surface brightness and redshift range of the \ferengi{} images, subdivided in bins corresponding to fixed ranges used for analysis in Figure~\ref{fig:p_vs_p}.}

@@

In Figure~\ref{fig:p_vs_p} we examine the change in $p_{\rm features}$ for the \ferengi{} galaxies relative to their lowest simulated redshift. In this analysis, only galaxies whose lowest simulated redshift image was ($\rm z_{sim}=0.3$) were used (see Table \ref{ferengivalues}), and only those which had detectable surface brightness measurements in \sextractor{}; this includes 3,959 of the total 6,466 images. For each simulated redshift value $z$, and at a fixed surface brightness $\mu$, we plot $p_{\rm features,z}$, the value measured at that simulated redshift, vs $p_{\rm features,z=0.3}$, the value measured for the same galaxy imaged at $z=0.3$.

Our objective is to use these data to predict, for a galaxy with a measured $p_{\rm features,z}$ value, what its $p_{\rm features}$ value \emph{would have been} if it had been viewed at $z=0.3$. This predicted value is defined as the debiased vote fraction $p_{\rm features,debiased}$, and is calculated by applying a correction to the measured value of $p_{\rm features}$, determined by the $\zeta$ function described in the previous section. A reliable predicted value can be obtained so long as the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ is single-valued; that is, for a given $p_{\rm features,z}$, there is exactly one corresponding value of $p_{\rm features}$ at $z=0.3$.

Figure~\ref{fig:p_vs_p} shows that the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ is \emph{not} always single valued; hence, it is not appropriate to correct galaxies that lie in certain regions of surface brightness/redshift/$p_{\rm features}$ space. These regions tend to have low $p_{\rm features}$ values at high redshift, but a wide range of values at $z=0.3$. These regions contain two morphological types of galaxies: First are genuine ellipticals, which have low values of $p_{\rm features}$ at both high and low redshift. Second are disks whose features become washed out at high redshift; hence their $p_{\rm features}$ value at $z=0.3$ may be quite high, while the value observed at high redshift is very low. This effect is strongest at high $z$ and low $\mu$, where features become nearly impossible to discern in the images.

@@

\begin{table*}
\caption{Breakdown of what we can correct out of the GZH data, by sample. \label{hubble_debiasable}}
\begin{tabular}{lrrrrrrr}
\hline\hline
                                   & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & SDSS    & Total \\
\hline
Correctable                        & 2,325   & 20,669 & 2,748 & 1,074  & 1,022   & 0       & 27,838\\
Uncorrectable                      & 1,403   & 19,626 & 1,832 & 271    & 980     & 0       & 24,112\\
No Correction Needed ($z \le 0.3$) & 967     & 11,693 & 1,190 & 280    & 247     & 37,545  & 51,922\\ 
NEI                                & 2,465   & 33,727 & 1,886 & 691    & 2,023   & 0       & 40,792\\
No Redshift Information            & 1,347   & 7,093  & 1,648 & 235    & 641     & 14,316  & 25,280\\
Total                              & 8,507   & 92,808 & 9,304 & 2,551  & 4,913   & 51,861  & 169,944\\
\hline\hline
\end{tabular}
\end{table*}

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
\caption{Distributions of redshift, surface brightness, and $p_{features}$ for correctable (purple), uncorrectable (green), and NEI (pink) galaxies in the full GZH sample. The uncorrectable galaxies tend towards higher redshift, slightly lower in surface brightness, and lower values of $p_{features}$ than the correctable galaxies. The long tail of NEI galaxies in redshift and surface brightness demonstrates the limits of the \ferengi{} sample, for which there is no data at $z>1$ or $\mu>24$.}
\label{fig:z_mu_p}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
\caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), uncorrectable (middle), and NEI (right) galaxies in the GZH sample.}

@@

%\subsection{Results of FERENGI analysis}
%
%{\bf Old text from Taiwan workshop}
%
%We show here the preliminary results of GZH classifications of images of galaxies placed at artificial redshifts. Figure~\ref{fig:ferengi_results_fake} shows the range of change of vote fractions for the change of $p_{\rm features}$ with redshift, for galaxies with different vote fraction levels, three ranges of surface-brightness levels and 7~evolutionary corrections (this last bit is indicated by the colour). 
%
%%-----------------------------------------------------------------------------------------------------------------------------------
%\begin{figure}
%\begin{center}
%
%\includegraphics[width=0.45\textwidth]{figures/somewhat_fake_results.pdf}
%
%\caption{Preliminary results of the \ferengi{} redshifting exercise. WARNING NO USER WEIGHTING.... For a range of vote fraction levels with three surface-brightness levels and 7 evolutionary corrections each (the colours indicate evolutionary correction value with green being $e=0$, we show the range of evolution of the vote fractions for featured vs. smooth with redshift.}
%
%\label{fig:ferengi_results_fake}
%
%\end{center}
%\end{figure}
%%-----------------------------------------------------------------------------------------------------------------------------------

@@

\subsection{Morphological measurements in GZH beyond Task 1}

@@

\subsection{Effect of changing depth for GOODS}

\subsection{SDSS Stripe 82 images}

\section{Catalog}

@@

Now people go and do science with these awesome GZH classifications.

@@

This project made heavy use of the Astropy packages in Python \citep{ast13}, as well as the seaborn plotting package \citep{was15}.

@@

Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S. Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England. The SDSS website is http://www.sdss.org/.
